{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-14 thesis/overview.tex
some new inspirational quotes

\inspirationalquote{
\begin{tabular}{p{0.83\textwidth}}
I see now that none of us are yet ready. The cycle exists so that we may improve ourselves. But
the one who reaches the summit is not our superior, for they stand on our shoulders to reach it.
\end{tabular}}
{The Shepherd v82.6.0174, The Talos Principle}

>>>>

%\inspirationalquote{
%\begin{tabular}{p{0.83\textwidth}}
%I see now that none of us are yet ready. The cycle exists so that we may improve ourselves. But
%the one who reaches the summit is not our superior, for they stand on our shoulders to reach it.
%\end{tabular}}
%{The Shepherd v82.6.0174, The Talos Principle}

\inspirationalquote{We pray to our ancestors. We've met all of them. None of them were better than anyone else.}
{Mina, Iconoclasts}

### 2018-08-14 thesis/related.tex
some new inspirational quotes

\chapter{Related Work}
\label{chap:relatedwork}
\inspirationalquote{
\begin{tabular}{p{0.58\textwidth}}
To test if your paper makes a genuine contribution to its discipline,
see if you can afford a generous tone in the "Related Work" section.
\end{tabular}}
{Conor McBride}

>>>>

\chapter{Related Work}
\label{chap:relatedwork}
%\inspirationalquote{
%\begin{tabular}{p{0.58\textwidth}}
%To test if your paper makes a genuine contribution to its discipline,
%see if you can afford a generous tone in the "Related Work" section.
%\end{tabular}}
%{Conor McBride}

\inspirationalquote{
\begin{tabular}{p{0.51\textwidth}}
It is important to draw wisdom from many different places.
If you take it from only one place, it becomes rigid and stale.
\end{tabular}
}
{Iroh, Avatar: The Last Airbender}
